### 2017-02-06 local-capability-machine.tex

              \begin{specification}[Malloc v.2]
                $c_\malloc$ satisfies the specification for malloc iff
                \[  
                  \begin{aligned}
                    &c_\malloc = ((\entry,\_),\_,\_,\_) \land\\
                    &\exists \iota_{\malloc,0} \ldotp \\
                    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (W) = \iota'.H (\iota'.s) ([i \mapsto W(i)]) ) \; \land \\
                    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
                    &\qquad \forall i, n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \\
                    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
                    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land\\
                    &\qquad \quad \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
                    &\qquad \quad \memreg(r_1) = \size \land \\
                    &\qquad \quad \size \geq 0 \land \\
                    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
                    &\qquad \quad \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\ %and this needs to change with ABI.
                    &\qquad \quad \Rightarrow \\
                    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
                    &\qquad \qquad \quad \exists j \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
                    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
                    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
                    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
                    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
                    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
                    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{(p,b,e,a)}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
                    &\qquad \qquad \qquad \size - 1 = e'-b' )
                  \end{aligned}
                \]
              \end{specification}
              In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.
              \lau{What about $c_\malloc$ and the value relation? Do we add this to the specification or try to prove it based on the specification?}

@@

\begin{lemma}[Malloc is safe to pass to adversary]
  \label{lem:malloc-in-vr}
  If $W(r) = \iota$ with $\iota \futurestr \iota_{\malloc,0}$, then
  $\npair{c_\malloc} \in \stdvr(W)$ for all $n$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

>>>>

              \begin{specification}[Malloc v.2]
                \label{spec:malloc}
                $c_\malloc$ satisfies the specification for malloc iff
                \[  
                  \begin{aligned}
                    &c_\malloc = ((\entry,\glob),\_,\_,\_) \land\\
                    &\exists \iota_{\malloc,0} \ldotp \\
                    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (\xi^{-1}(W)) = \iota'.H (\iota'.s) (\xi^{-1}([i \mapsto W(i)])) ) \; \land \\
                    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
                    &\qquad \forall i, n, \size \in \nats \ldotp \forall
                    w_{\var{ret}} \in \Words \ldotp \\
                    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
                    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
                    &\qquad \quad \memreg(r_1) = \size \land \size \geq 0 \land  \memreg(r_0) = w_{\var{ret}} \land \\
                    &\qquad \quad \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\ %and this needs to change with ABI.
                    &\qquad \quad \Rightarrow \\
                    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
                    &\qquad \qquad \quad \exists j \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
                    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
                    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
                    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
                    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
                    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
                    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
                    &\qquad \qquad \qquad \size - 1 = e'-b' ) \land\\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp (\memreg(r_1)
                    \not\in \ints \vee \memreg(r_1) < 0) \land \memreg(\pcreg) = \updatePcPerm{c_\malloc} \Rightarrow \exists j \in \nats \ldotp \Phi \step[j] \failed)
                  \end{aligned}
                \]
              \end{specification}
              In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.
              \lau{What about $c_\malloc$ and the value relation? Do we add this to the specification or try to prove it based on the specification?}

@@

\begin{lemma}[Malloc is safe to pass to adversary]
  \label{lem:malloc-in-vr}
  If $W(r) \futurestr \iota_{\malloc,0}$, then
  $\npair{c_\malloc} \in \stdvr(W)$ for all $n$.
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item $c_\malloc = ((\entry,\glob),\base,\addrend,\addr)$.\\
    By: the malloc specification (Specification~\ref{spec:malloc}).
  \item Suffices: $\npair{(\start,\addrend,\addr)}\in\entryCond{\glob}(W)$.\\
    By definition of $\stdvr(W)$.
  \item Assume: $n' < n$, $W'\futurestr W$.\\
    Suffices: $\npair[n']{((\exec,\glob),\start,\addrend,\addr)} \in
    \stder(W')$.\\
    By: definition of the $\entryCond{}$
  \item Assume: $n''\leq n'$,
    $\npair[n'']{\reg}\in\stdrr(W')$, $\heapSat[\ms]{n''}{W'}$\\
    Suffices:
    $\npair[n'']{(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms)}\in\observations(W')$\\
    By: definition of $\stder(W')$
  \item Assume: $i < n''$,
    $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[i]
    (\halted,\mem')$\\
    Suffices: $\exists W''\futurestr W',\ms_r,\ms'\ldotp$ $\mem' =
    \ms'\uplus\ms_r\uplus\ms_f$ and $\heapSat[\ms']{n-i}{W''}$\\
    By: definition of $\observations(W')$
  \item $W'(r) \futurestr \iota_{\malloc,0}$\\
    Easy from: $W'\futurestr W$ and $W(r) \futurestr \iota_{\malloc,0}$ using
    transitivity of $\futurestr$.
  \item $\exists P : \activeReg{W'} \rightarrow \HeapSegments \ldotp$
    $\memSatPar[n'']{\ms}{W'}{P}$, i.e. $\hs = \biguplus_{r\in\activeReg{W'}}P(r)$ and
    $\forall r \in \activeReg{W'} \ldotp$ $\exists H,s \ldotp$ $W'(r) =
    (\_,s,\_,\_,H)$ and $\npair[n'']{P(r)} \in H(s)(\xi^{-1}(W'))$\\
    By: definition of $\heapSat[\ms]{n''}{W'}$.
  \item Define $\ms_{\var{frame}} = \left(\biguplus_{r'\in\activeReg{W'},r'\neq
        r}P(r')\right)\uplus\ms_f$. Then $\ms\uplus\ms_f = P(r) \uplus
    \ms_{\var{frame}}$ and $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}(W'))}$.
    Easy from the previous point.
  \item $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}([r\mapsto W'(r)]))}$, i.e.
    $\heapSat[P(r)]{n''}{[r\mapsto W'(r)]}$.\\
    By: the malloc specification (Specification~\ref{spec:malloc}) from the
    previous point.
  \item Case: $\reg(r_1) \in \ints$ and $\reg(r_1) \geq 0$
    \begin{enumproof}
    \item Define $\var{size} = \reg(r_1)$
    \item $\exists \Phi' \in \ExecConfs, \ms_{\var{footprint}}',
      \ms_{\var{alloc}} \in \HeapSegments, j \in \nats, b',e'\in \Addrs,
      \iota_\malloc' \in \Regions \ldotp$
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)
      \step[j] \Phi'$ and $\memheap[\Phi']=\ms_{\var{footprint}}' \uplus
      \hs_{\var{alloc}} \uplus \ms_{\var{frame}}$ and $\iota_{\malloc}'
      \futurewk W'(r)$ and $\heapSat[\ms_{\var{footprint}}']{n-j}{[r \mapsto
        \iota_\malloc']}$ and $\dom(\hs_{\var{alloc}}) = [b',e']$ and $\forall a
      \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0$ and $\memreg[\Phi'] =
      \memreg[\Phi]\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\update{r_1}{((\rwx,\glob),b',e',b')}$
      and $\var{size} - 1 = e'-b' )$.\\
      By: the malloc specification (Specification~\ref{spec:malloc}).
    \item Define $W'' = W'\update{r}{\iota_\malloc'}[i\mapsto
      \iota^\nwl_{b',e'}]$ for $i \not\in\dom(W')$
    \item \dominique{TODO}
    \end{enumproof}
  \item Case: $\reg(r_1)\not\in\ints \vee \reg(r_1) < 0$
    \begin{enumproof}
    \item $\exists j\ldotp (\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[j]
      \failed$\\
      By: the malloc specification (Specification~\ref{spec:malloc}).
    \item Contradiction with 
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[i]
      (\halted,\mem')$
    \end{enumproof}
  \end{enumproof}
\end{proof}
